The \project{unRAVE} catalog

### 2016-09-08 article/unrave.tex
some text

After verifying that our atmospheric parameters and abundances are comparable with other
high-resolution studies, here we verify that the abundances we find
are consistent with expectations from astrophysics.  One example is globular clusters, 
which show anti-correlations in light element abundances 
\citep[e.g.,][and references therein]{Norris_Da_Costa_1995,Carretta_2009}.  In the \rave\
survey, \cite{Anguiano_2015} identified 70 stars with positions and radial velocities that are
consistent with being members of globular clusters: 49 stars belonging to NGC~5139
($\omega$~Centauri), 11 members of the retrograde globular cluster NGC~3201, and 10 
members of NGC~362. In addition to these systems, 12 stars thought to belong to NGC~1851
were found in the \rave\ data by \cite{Kunder_2014}, and a further 10 stars in NGC~6752.  
We refer the reader to those studies for details regarding the membership selection.

In Figure~\ref{fig:globular-cluster-HRD} we show the effective temperature
$\teff$ and surface gravity $\logg$ for pre-defined members of globular clusters in \rave.
The top panels indicate measurements made in this work, and for comparison purposes we have included
the results from the fourth \rave\ data release.  We show representative \project{PARSEC} isochrones 
\citep{Bressan_2012} in all panels, where the isochrone ages and metallicities are adopted from
\citet{Kunder_2016,Marin-Franch_2009}, and the \citet[][accessed 6 September 2016]{Harris_1996} 
online catalog of globular cluster properties.  The globular cluster with the most number of
\rave\ members is NGC~5139 ($\omega$-Centauri), where we find a significant metallicity spread
consistent with high-resolution studies \citep{Marino_2011,Carretta_2009,Carretta_2013}.  We
find the mean metallicity of prescribed $\omega$-Centauri members to be $[{\rm Fe/H}] = -0.85$.
However, it is clear that the membership criteria could be improved with our
revised metallicities and detailed chemical abundances. 
Indeed, this demonstrates that our abundance labels can be used to identify
globular cluster members that are now tidally disrupted \citep{Anguiano_2016,Kuzma_2016,Navin_2016},
even for stars with low S/N ratios.

@@

The \rave\ survey observed $\sim$160 highly probable members of several open clusters:
78 stars in the Pleiades, 26 in Hyades, 30 stars in the solar-metallicity cluster
M67 and 13 stars in IC4651. Details on the open cluster membership and selection can 
be found in \cite{Kunder_2016}.  We show the effective temperature $\teff$ and surface
gravity $\logg$ for these stars in Figure \ref{fig:open-cluster-HRD}.  The isochrones
are sourced from \citet{Bressan_2012}, with cluster properties adopted from 
\cite{Kunder_2016} and \cite{Kharchenko_2013}.

We find good agreement between our atmospheric parameters (top panels) and the 
isochrones shown.  The position of the red clump in IC4651 and M67 are perfectly matched
to the isochrone, and the Hyades main-sequence is in good agreement down to 
$T_{\rm eff} \approx 4000$~K.  Similarly, we find consistency with the literature and
our metallicity scale.  We find the mean metallicity of M67 stars to be 
$[{\rm Fe/H}] = -0.02 \pm 0.17$~dex (30 stars), in excellent agreement with the
expected $[{\rm Fe/H}] = 0.00$ value (not accounting for atomic diffusion).
We further find the Hyades mean metallicity to be $[{\rm Fe/H}] = 0.07 \pm 0.09$~dex,
consistent with \citet{Paulson_2003}: $[{\rm Fe/H}] \approx 0.13$.
For IC4651 from 13 stars we find a mean $[{\rm Fe/H}] = 0.15 \pm 0.12$~dex, matching the
high-resolution, high S/N study of \citet{Pasquini_2004}, where they find 
$[{\rm Fe/H}] = 0.10 \pm 0.03$~dex. Finally, from 78 stars we find the mean
metallicity of the Pleiades to be $[{\rm Fe/H}] = -0.02 \pm 0.12$~dex, in agreement
with the $[{\rm Fe/H}] = -0.034 \pm 0.024$~dex measurement reported by 
\citet{Friel_Boesgaard_1990}.

The most pronounced discrepancy is seen in the main-sequence of the Pleiades.
Like \citet{Kordopatis_2013}, we find lower $\logg$ values than what the isochrone
shown predicts.  \stub{Hawkins: use correct isochrone from Bouy to see if this issue is resolved.}
%  Firstly,
%we note that theoretical isochrones often struggle to match the observed
%color-magnitude diagrams for some young clusters \citep[e.g., the Pleiades, see][]{Bouy_2015}.

@@

\bibitem[Norris \& Da Costa(1995)]{Norris_Da_Costa_1995} Norris, J.~E., \& Da Costa, G.~S.\ 1995, \apj, 447, 680

>>>>

After verifying that our atmospheric parameters and abundances are comparable 
with other high-resolution studies, here we verify that the abundances we find
are consistent with expectations from astrophysics.  In the \rave\ survey, 
\cite{Anguiano_2015} identified 70 stars with positions and radial velocities that are
consistent with being members of globular clusters: 49 stars belonging to NGC~5139
($\omega$~Centauri), 11 members of the retrograde globular cluster NGC~3201, and 10 
members of NGC~362. In addition, \citet{Kunder_2014} compiled 12 stars thought to 
belong to NGC~1851, and a further 10 stars in NGC~6752.  We refer the reader to 
those studies for details regarding the membership selection.

In Figure~\ref{fig:globular-cluster-HRD} we show our effective temperature
$\teff$ and surface gravity $\logg$ for these prescribed globular cluster members.
The right-hand panels indicate measurements made in this work, and for comparison 
purposes we have included the results from the fourth \rave\ data release in the 
left-hand panels.  We show representative \project{PARSEC} isochrones 
\citep{Bressan_2012} in all panels, where the isochrone ages and metallicities 
are adopted from \citet{Kunder_2016,Marin-Franch_2009}, and the 
\citet[][accessed 6 September 2016]{Harris_1996} online catalog of globular 
cluster properties.  The globular cluster with the most number of members is 
NGC~5139 ($\omega$-Centauri), where we find a significant metallicity spread
consistent with high-resolution studies \citep{Marino_2011,Carretta_2009,Carretta_2013}. 
Based on the pre-defined membership criteria, we find the mean metallicity
of $\omega$-Centauri to be $[{\rm Fe/H}] = -0.85$.  However, it is clear that the 
membership criteria could be improved with our revised metallicities and 
detailed chemical abundances.  Indeed, our individual abundance labels could 
be used to identify globular cluster members that are now tidally disrupted 
\citep{Anguiano_2016,Kuzma_2016,Navin_2016}, even for stars with low S/N ratios.

@@

The \rave\ survey observed $\sim$160 highly probable members of several open clusters:
78 stars in the Pleiades, 26 in Hyades, 30 stars in the solar-metallicity cluster
M67, and 13 stars in IC4651. Details on the open cluster membership and selection can 
be found in \cite{Kunder_2016}.  We show the effective temperature $\teff$ and surface
gravity $\logg$ for these stars in Figure \ref{fig:open-cluster-HRD}.  The isochrones
are sourced from \citet{Bressan_2012}, with cluster properties adopted from 
\cite{Kunder_2016} and \cite{Kharchenko_2013}.

We find good agreement between our atmospheric parameters (right-hand panels) and the 
isochrones shown.  The position of the red clump in IC4651 and M67 are perfectly matched
to the isochrone, and the Hyades main-sequence is in good agreement down to 
$T_{\rm eff} \approx 4000$~K.  Similarly, we find consistency with the literature and
our metallicity scale.  We find the mean metallicity of M67 stars to be 
$[{\rm Fe/H}] = -0.02 \pm 0.03$~dex, in excellent agreement with the expected 
$[{\rm Fe/H}] = 0.00$ value (not accounting for atomic diffusion).
We further find the Hyades mean metallicity to be $[{\rm Fe/H}] = 0.07 \pm 0.09$~dex,
consistent with \citet{Paulson_2003}: $[{\rm Fe/H}] \approx 0.13$.
For IC4651 from 13 stars we find a mean $[{\rm Fe/H}] = 0.15 \pm 0.03$~dex, matching the
high-resolution, high S/N study of \citet{Pasquini_2004}, where they find 
$[{\rm Fe/H}] = 0.10 \pm 0.03$~dex. Finally, from 78 stars we find the mean
metallicity of the Pleiades to be $[{\rm Fe/H}] = -0.02 \pm 0.01$~dex, in very 
good agreement with the $[{\rm Fe/H}] = -0.034 \pm 0.024$~dex measurement reported by 
\citet{Friel_Boesgaard_1990}.

Despite the discrepancies between the isochrone and our derived labels for stars
in the Pleiades, we have made no attempt to refine the membership selection in
any of the aforementioned clusters.  We note however, that the same discrepancy
with the isochrone appears present in the fourth \rave\ data release \citet{Kordopatis_2013}.

@@

%\bibitem[Norris \& Da Costa(1995)]{Norris_Da_Costa_1995} Norris, J.~E., \& Da Costa, G.~S.\ 1995, \apj, 447, 680
